\EVOSUITE at the SBFT 2023 Tool Competition

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Rest of About EvoSuite section

\EVOSUITE implements various evolutionary algorithms that operate on this
representation. The initial approach was to optimise entire test suites with
respect to their overall code coverage~\cite{GoA_TSE12}. However, after
extensive evaluation~\cite{ea_evaluation} the default is now the
\emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
algorithm~\cite{dynamosa}, which operates at the test case level.

The search is driven by fitness functions that encode coverage criteria.
\EVOSUITE can optimise for several criteria simultaneously, and the core fitness
functions in \EVOSUITE are based on traditional heuristics for code coverage, such
as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
However, there are several further fitness functions based on mutation
testing~\cite{emse14_mutation} as well as other basic
criteria~\cite{rojas2015combining}.

@@

\EVOSUITE is also heavily optimised in order to produce tests that are as
readable as possible and avoid test smells~\cite{panichella2020revisiting}.
For this, \EVOSUITE applies post-processing once the available search budget
has been exhausted~\cite{FrA11c,FrA13a}, consisting of minimisation to
remove redundant tests and statements, and adding a minimised set of assertions
using mutation analysis~\cite{10.1109/TSE.2011.93}.

>>>>

\EVOSUITE implements various evolutionary algorithms that operate on this
representation. Early versions of \EVOSUITE followed the \emph{Whole Test Suite} (WTS)
approach~\cite{GoA_TSE12}, where entire test suites are optimised with
respect to their overall code coverage. However, a subsequent study~\cite{ea_evaluation}
found the \emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA)~\cite{dynamosa}
to yield superior results. Unlike WTS, DynaMOSA operates directly at the test case level,
and it is now the default algorithm in \EVOSUITE.

Irrespective of which algorithm is chosen, the search is always driven by fitness
functions. These encode coverage criteria, and \EVOSUITE can optimise for multiple
criteria at the same time. Core fitness functions are based on traditional heuristics
for code coverage, such as branch distance and approach level (see ~\cite{GoA_TSE12} for more details.)
Besides this, there are further fitness functions based on mutation
testing~\cite{emse14_mutation} and other basic criteria~\cite{rojas2015combining}.

@@

Once the available search budget for the main phase has been exhausted,
\EVOSUITE can be configured to run a postprocessing phase where tests are optimised for
readability~\cite{FrA11c,FrA13a}. This includes avoiding test
smells~\cite{panichella2020revisiting}, minimisation to remove redundant tests
and statements, and adding a minimised set of assertions using mutation
analysis~\cite{10.1109/TSE.2011.93}.
